### 2013-10-30 proposal/proposal/chapter2.tex
changes

\section{Types of Dialogue Games}\label{sec:DialogueGames}

\section{Negotiation Dialogue Games}\label{sec:Negotiation}
Negotiation is a form of interaction in which a group of self-interested agents with conflicting interests and a desire to cooperate attempt to
reach  a mutual acceptable agreement on the division of scarce resources.

   \subsection{Negotiation Component}\label{sec:NComp}

   \subsection{Approaches to Automated Negotiation}\label{sec:Nappro}

>>>>

    \section{Community of Web Services}\label{sec:CommunityWS}

        \subsection{Web Services}\label{sec:WS}

        \subsection{Definition}\label{sec:CWSDefinition}

        \subsection{Architecture}\label{sec:CWSArchitecture}

        \subsection{Operations}\label{sec:CWSOperations}

            \subsubsection{Community Development}\label{sec:CWSCommunityDev}

            \subsubsection{Web Service Attraction and Retention}\label{sec:CWSAttraction}

            \subsubsection{Web Service Selection}\label{sec:CWSSelection}

    \subsection{Related Work}\label{sec:CWSRelatedWork}
